A survey on NoSQL and NewSQL datastores

### 2014-11-18 paper_dec/tabel.tex
tabel in paper + TODOs

\documentclass{article}
\usepackage{graphicx}
\usepackage{pdflscape}
\usepackage{rotating}
\usepackage[a4paper,margin=.5in,landscape]{geometry}
\usepackage{booktabs}
\usepackage{array}
\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}

\begin{document}
%\begin{landscape}
% Table generated by Excel2LaTeX from sheet 'Sheet1'
% Please add the following required packages to your document preamble:
% \usepackage{booktabs}

@@

\multicolumn{1}{|l|}{\textbf{Concurrency control}} & Atomic single document operations, otherwise 2-phase commit{[}10{]} Concurrent reads, exclusive writes (lock on DB level) & CQL offers CAS, row-level atomicity & Single-row transactions (ACID), OCC with MVCC for wider scope operations & Application can implement optimistic (using CAS) or pessimistic concurrency control &                                     & ACID + data access serialized and executed in single-threaded environment

@@

%\end{landscape}
\end{document}

>>>>

\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}

\begin{landscape}

@@

\multicolumn{1}{|l|}{\textbf{Concurrency control}} & Atomic single document operations, otherwise 2-phase commit{[}10{]} Concurrent reads, exclusive writes (lock on DB level) & CQL offers CAS, row-level atomicity & Single-row transactions (ACID), OCC with MVCC for wider scope operations & Application can implement optimistic (using CAS) or pessimistic concurrency control &                                     & ACID + data access serialized and executed in single-threaded environment \\ \midrule
\multicolumn{1}{|l|}{\textbf{Open-source?}}              & Y                                                                                                                                                               & Y                                                                                                                        & Y                                                                                  & Y                                                                                   & Y                                   & Y                                                                        

@@

\end{landscape}
